Deep Reinforcement Learning for Conservation Decisions

### 2021-05-12 manuscript/manuscript.Rmd
Almost done with value learning bit

## Value Learning
Another way to approach the RL problem is by estimating a value function, and using the value function to retrieve a policy. 
Value functions attempt to quantify the goodness of being in a state or taking an action from a state.
Given that the objective of RL is to maximize the cumulative expected reward, "goodness" refers to the likelihood that a state or state-action pair will result in a high cumulative reward trajectory.
The state-action-value or Q function finds the expected return provided a state and action,

@@

The general motivation is that if we know the Q function, then we can easily find the optimal action at any state by selecting the action with the highest Q-value: $a_t^* = \underset{a_t}{\text{argmax}} \, Q^\pi (s_t, a_t)$.
In the case that the state-action space can be tractably represented in a table, one could employ an algorithm, like temporal-difference control -- see Sutton Ch. 6 for details -- which approximates the Q value for every state-action pair [@suttonbarto]. 
Yet, for many decision-making problems, the state-action space cannot be tractably represented in a table; one effective alternative for this case is to use a neural network to approximate the Q-function.

>>>>

## Value Learning
Another way to approach the RL problem is by estimating a value function, and then using the value function to retrieve a policy. 
Value functions attempt to quantify the goodness of being in a state or taking an action from a state.
Given that the objective of RL is to maximize the cumulative expected reward, "goodness" refers to how high of a cumulative reward the agent can expect to receive.
For example, the state-action-value or Q function finds the expected return from a state and action pair under a policy, $\pi$,

@@

The general motivation is that if we know the Q function under the condition that the given policy visits all state-action pairs [@suttonbarto 131; @Qproof], then we can easily find the optimal action at any state by selecting the action with the highest Q-value: $a_t^* = \underset{a_t}{\text{argmax}} \, Q^\pi (s_t, a_t)$.
In the case that the state-action space can be tractably represented in a table, one could employ a  algorithm, like temporal-difference control -- see Sutton Ch. 6 for details -- which approximates the Q value for every state-action pair [@suttonbarto]. 
Yet, for many decision-making problems, the state-action space cannot be tractably represented in a table; one effective alternative for this case is to use a neural network to approximate the Q-function, a method called deep Q-learning. 
The general process for deep Q-learning differs from policy gradient methods, since instead of trying to maximize the return directly, the objective is to minimize the Bellman error.
The Bellman error
